%%%%%%%%%%%%%%%%%
% This CV created using altacv.cls
% (v1.6.4, 13 Nov 2021) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% Use the "normalphoto" option instead of "ragged2e,withhyper" if you want a normal photo instead of cropped to a circle
\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
%% AltaCV uses the fontawesome5 and packages.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=0.8cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
% \definecolor{SlateGrey}{HTML}{2E2E2E}
% \definecolor{LightGrey}{HTML}{666666}
% \definecolor{DarkPastelRed}{HTML}{450808}
% \definecolor{PastelRed}{HTML}{8F0D0D}
% \definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{black}
\colorlet{heading}{black}
\colorlet{headingrule}{black}
\colorlet{subheading}{black}
\colorlet{accent}{black}
\colorlet{emphasis}{black}
\colorlet{body}{black}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Ilia Kuznetsov}
\tagline{Software Development Engineer}

%% You can add multiple photos on the left or right
% \photoR{2.8cm}{Globe_High}
% \photoL{2.5cm}{Yacht_High,Suitcase_High}

\personalinfo{
  \location{Dublin, Ireland}
%   \mailaddress{Åddrésş, Street, 00000 Cóuntry}
  \email{ikuz2002@gmail.com}
%   \phone{+79117500058}
  \linkedin{kuzznya}
  \github{kuzznya}
  %% You can add your own arbitrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}[https://example.com/]
  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
  %%
  %% For services and platforms like Mastodon where there isn't a
  %% straightforward relation between the user ID/nickname and the hyperlink,
  %% you can use \printinfo directly e.g.
  % \printinfo{\faMastodon}{@username@instace}[https://instance.url/@username]
}

\makecvheader
%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.64}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}
\cvsection{Experience}

\cvevent{Software Development Engineer}{Amazon Web Services}{Nov 2022 -- Ongoing}{Dublin, Ireland}

AWS ElastiCache – managed Redis, Valkey and Memcached service

\begin{itemize}
  \item Implemented SQL migration validation framework with a DDL statement parser that allowed full CD automation of database migration.
  \item Improved vertical scaling and engine upgrade framework, ensuring zero downtime and 99.99\% availability.
  \item Designed and delivered data lake based analysis and reporting for End-of-Life campaigns that allowed customers to see affected resources.
  \item Implemented service update support for ElastiCache Serverless that updates customers' clusters automatically and transparently to the customer. 
\end{itemize}

\divider

%\cvevent{}{Dell Technologies}{}{St. Petersburg, Russia}
\cvevent{Senior Java Developer}{Dell Technologies}{Mar 2022 -- Jul 2022}{}
\cvevent{Java Developer}{}{May 2021 -- Mar 2022}{St. Petersburg, Russia}

System security management project that manages host patching, credential rotation \& other security-related tasks.
\begin{itemize}
  \item Designed and implemented new event driven architecture using Kafka, significantly improving reliability of the system.
  \item Improved observability of the system by introducing tracing and structured logging.
\end{itemize}

Java, Sprint Boot, K8s, RabbitMQ, Kafka, PostgreSQL, ELK

\divider

\cvevent{Junior Java Developer}{Intellectual Technologies}{Nov 2020 -- May 2021}{St. Petersburg, Russia}

Data collecting \& analysis system for oil industry.
\begin{itemize}
  \item Designed and implemented fault-tolerant and efficient data collecting and processing from the data sensors, handling over 20k values/sec.
  \item Implemented stream and batch analysis that provided monitoring of the critical parts of the oil well.
  \item Designed a long-term storage solution for collected data (over 1TB/day).
\end{itemize}

\divider

\cvevent{Junior Java Developer}{ALPE Consulting}{Dec 2019 -- May 2021}{}
\cvevent{Intern Java Developer}{}{Jul 2019 -- Dec 2019}{St. Petersburg, Russia}

Developed an extension system for SAP using microservice architecture. The communication with SAP was set up with SOAP protocol. Created both backend and frontend part, used microfrontend approach.\\
Java, Spring Boot, Spring Cloud, Hibernate, Vue.js

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Education}

\cvevent{\normalsize{BSc, Software Engineering}}{ITMO University}{Sept 2019 -- June 2023}{}

\cvsection{Skills}

\cvevent{Programming Languages}{}{}{}

\cvtag{Java}
\cvtag{Kotlin}
\cvtag{Go}
\cvtag{SQL}
\cvtag{JavaScript/TypeScript}
\cvtag{Python}
\cvtag{Ruby}
\cvtag{Bash}

\cvevent{Technologies}{}{}{}

\cvtag{PostgreSQL}
\cvtag{Cassandra}
\cvtag{MongoDB}
\cvtag{Redis}
\cvtag{Kafka}
\cvtag{RabbitMQ}
\cvtag{InfluxDB}
\cvtag{DynamoDB}

\vspace{0.2cm}

\cvevent{Tools}{}{}{}

\cvtag{AWS}
\cvtag{Terraform}
\cvtag{Docker}
\cvtag{Kubernetes}
\cvtag{Linux}
\cvtag{Git}
\cvtag{GitHub Actions}
\cvtag{Jenkins}


\cvsection{Languages}

\begin{itemize}
\item English - advanced
\item Russian - native
\item French - beginner
\end{itemize}

\cvsection{Projects}

\cvevent{Redis Search Replica (Go)}{}{}{}

Redis full text search support implemented as a separate read replica (Go, C, k6)

\github{kuzznya/go-redis-search-replica}

\divider

\cvevent{Letsdeploy}{Deploy apps \& services to K8s through UI}{}{}
\github{kuzznya/letsdeploy}

Project provides an easy way to deploy apps and services (PostgreSQL, Redis, etc.) to Kubernetes using web UI (Go, Vue.js)

%% Yeah I didn't spend too much time making all the
%% spacing consistent... sorry. Use \smallskip, \medskip,
%% \bigskip, \vspace etc to make adjustments.

\end{paracol}

\end{document}
